%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Marcelo Ponce}{}
\email{marcelo.ponce.ardon@gmail.com}
\phone[mobile]{(587) 718 6272}
\address{Toronto, ON}


\begin{document}

\recipient{}{Hiring Manager at Inworld AI}
               % Department of Computer Application,\\
               % Full Address (State)}
\date{\today}
\opening{\textbf{Sub: Application for Unreal Engine Software Engineering Intern - Canada}}
\closing{With gratitude,}


%\enclosure[Enclosed (Marksheets/Certificates)]{
%              \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                 \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                 2. Diploma (MarkSheet/Certificate)
%                 \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                 3. B.Tech (MarkSheet/Certificate)
%                 \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                 4. M.Tech (MarkSheet/Certificate)
%                 \hspace{2.1em} 8. Caste Certificate \\
%                 }
\makelettertitle

Hi Inworld Team,

My name is Marcelo (Mars) Ponce, and I'm a non-binary Latine technologist and recent computer science graduate. I'm thrilled that you're looking to grow your team and I'm reaching out because I'm looking to gain experience in building interactive, intelligent systems and I have a genuine desire to grow in the game and AI space with the passionate crew at Inworld AI.

I’ve always been fascinated by the way technology can shape how we share our lived experiences, tell stories and foster connections, understanding and empathy. As someone who didn’t grow up seeing people like me in tech or game development, I’ve had to navigate a lot of uncertainty. But it also taught me to lean into curiosity and keep creating, even when I wasn’t sure if I belonged. That same energy is what drives me to want to be part of a team like yours.

While reading Kylan's article "A Return to the User", the way they described the shift towards prioritizing human-centered design and true interactivity in AI experiences mirrors the ideals I’ve been striving toward in my own work. I’ve always believed that technology, especially in gaming and interactive experiences, should make our interactions richer, our choices meaningful, and foster our creativity, so I'm enthusiastic about learning more about how your AI library will be able to enrich user experience in Unreal. This perspective of AI as a tool that amplifies human potential, rather than replaces it, really resonated with me. It made me even more excited about the possibility of contributing to a team that sees AI as a way to connect people.

While I am in the early stages of my career, I think this is the perfect building block to contribute to a small passionate team where I will be able to come some amazing impacts in just a few months. I have spent the last few years working with object oriented programing, parallel programming in C/C++ and other software development concepts that I'm eager to implement in the game dev industry. I’m especially excited about the chance to work with generative AI tools inside Unreal. That intersection feels like where the future of storytelling and interaction is headed, and I want to help build it.

I’m confident in my foundation in C++, data structures, and algorithms, and more importantly, I’m eager to learn. I'm seeking mentorship and would be honored to learn from your engineers while also bringing my own perspective, questions, and drive to the table.

Thank you for taking the time to read my application. I’m ready to contribute, learn, and build something meaningful with your team.


\vspace{0.5cm}

\makeletterclosing

\end{document}
