%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% Adapted for Software Internship Position
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{resume} % Use the resume class

%\usepackage{ebgaramond} % Optional: Use the EB Garamond font
\usepackage{hyperref} % Optional: Add hyperlink support

%------------------------------------------------

\name{Marcelo Ponce} % Your name
\address{Toronto, ON} % Your address
\address{(587)~$\cdot$~718~$\cdot$~6272 \\ \href{mailto:marcelo.ponce.ardon@gmail.com}{marcelo.ponce.ardon@gmail.com} \\ \href{https://github.com/marceloponceardon}{github.com/marceloponceardon}} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% PROFILE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Profile}
%	Enthusiastic Computer Science student passionate about backend development and AI-driven solutions. Proven ability to collaborate effectively in teams and deliver high-quality, sustainable code. Seeking to contribute to cutting-edge projects in a dynamic software development environment.
%\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{University of Toronto, Mississauga (UTM)} \hfill \textit{September 2019 - June 2025} \\
	Honours Bachelor of Science (HBSc) \\
	Computer Science Specialist, Minor in Mathematics \\
	\begin{rSubsection}{\textbf{Relevant Coursework}}{}{}{}
		\item CSC427: Computer Security
		\item CSC413: Neural Networks \& Deep Learning
		\item CSC409: Scalable Computing
		\item CSC373: Algorithm Design, Analysis \& Complexity
		\item CSC367: Parallel Programming
		\item CSC343: Introduction to Databases
		\item CSC309: Programming on the Web
		\item CSC301: Introduction to Software Engineering
	\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

	\textbf{Programming Languages:} Python, C/C++, Java, Go, SQL, HTML/CSS, JavaScript \\
	\textbf{Tools \& Technologies:} Docker, RESTful APIs, LaTeX, React, Node.js, Redis \\
	\textbf{IDEs \& Editors:} Vim, Visual Studio Code, Eclipse \\
	\textbf{Version Control:} Git, GitHub \\
	\textbf{Databases:} PostgreSQL, MySQL, SQLite, Cassandra \\
	\textbf{CI/CD:} Github Actions \\
	\textbf{Other Skills \& Tools:} Linux, Data Modeling, Automated Testing, Amazon Web Services (AWS) Agile Development, Scrum

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{CTF427}{University of Toronto}{CSC427 - \href{https://github.com/marceloponceardon/CTF427}{github.com/marceloponceardon/CTF427}}{January 2025 - March 2025}
		\item	\textbf{Description:} A competitive Capture the Flag (CTF) event designed to teach students about common security vulnerabilities and exploit techniques.
		\item	\textbf{Technologies:} VirtualBox, PostgreSQL, Docker, CTFd, EJS, JavaScript, HTML/CSS, C, Python, Kali Linux.
		\item	\textbf{Responsibilities:} Designed and implemented a CTF event for the course. Developed challenges using various programming languages and tools. Created a web-based platform using CTFd to host the event. Integrated PostgreSQL for data storage and Docker for containerization. Hosted the event on VirtualBox and taught students how to use Kali Linux for relevant challenges.
	\end{rSubsection}

	\begin{rSubsection}{\href{https://jules-ferguson.com}{jules-ferguson.com}}{Jules Ferguson}{Personal - \href{https://github.com/marceloponceardon/jules-ferguson.com}{github.com/marceloponceardon/jules-ferguson.com}}{June 2024 - On Going}
		\item	\textbf{Description:} Personal website for Jules Ferguson, a Toronto-based photographer and sexual health educator.
		\item	\textbf{Technologies:} Node.js, Express, HTML/CSS, JavaScript, Vercel, Render, GitHub Actions.
		\item	\textbf{Responsibilities:} Developed a RESTful API using Node.js and Express. Integrated GitHub Actions for CI/CD. Hosted on Vercel and Render. Integrate google photos and google drive API for image and video storage easily accessible for the client.
	\end{rSubsection}

	\begin{rSubsection}{Opalescence}{University of Toronto}{CSC301 - \href{https://github.com/opalescencelabs}{github.com/opalescencelabs}}{January 2024 - April 2024}
		\item	\textbf{Description:} Web-based sharable note-taking application.
		\item	\textbf{Technologies:} GoLang, PostgreSQL, Redis, TypeScript, React, Docker, GitHub Actions, Google OAuth2.0.
		\item	\textbf{Responsibilities:} Implemented a RESTful API using GoLang (GinGonic) and PostgreSQL (GORM) Integrated hosted Redis for caching responses. Integrated GitHub Actions for CI/CD. Google OAuth2.0 for user authentication. Hosted on Vercel, OnRender, and ElephantSQL.
	\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

	\begin{rSubsection}{Barista}{March 2023 - Present}{Claudia's Coffee}{Toronto, ON}
		\item Prepared custom espresso drinks and specialty seasonal beverages in a fast paced environment, making up to 45 drinks per hour.
		\item Maintained and cleaned equipment daily, ensuring machine longevity and beverage quality.
		\item Adjusted espresso grind at various times throughout the day to maintain consistent shot quality.
		\item Opening and closing independently of supervision, cash handling, ordering inventory, arming alarms.
		\item Developed relationships with customers, connecting management with local businesses.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Barista}{January 2022 - March 2023}{Touti Gelati}{Toronto, ON}
		\item Prepared over 30 beverages and desserts daily, maintaining high quality and presentation standards.
		\item Enhanced customer experience by providing tailored recommendations for gelato and specialty drinks.
		\item Managed inventory for daily operations, ensuring availability of ingredients during peak hours.
	\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
% LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}
	\begin{rSubsection}{}{}{}{}
		\item \textbf{English} | Advanced
		\item \textbf{Spanish} | Native
	\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
