%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Marcelo Ponce}{}
\email{marcelo.ponce.ardon@gmail.com}
\phone[mobile]{(587) 718 6272}
\address{Toronto, ON}


\begin{document}

\recipient{}{Hiring Manager at Sentry}
               % Department of Computer Application,\\
               % Full Address (State)}
\date{\today}
\opening{\textbf{Sub: Application for Software Engineer, New Grad (2025)}}
\closing{With gratitude,}


%\enclosure[Enclosed (Marksheets/Certificates)]{
%              \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                 \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                 2. Diploma (MarkSheet/Certificate)
%                 \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                 3. B.Tech (MarkSheet/Certificate)
%                 \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                 4. M.Tech (MarkSheet/Certificate)
%                 \hspace{2.1em} 8. Caste Certificate \\
%                 }
\makelettertitle

Hi Sentry Team,

I'm Marcelo (Mars) Ponce, a recent computer science graduate and enthusiastic backend developer excited about Sentry’s mission to help developers ship better software, faster. What drew me to this role is how clearly it blends real impact, mentorship, and technical challenge, all in a modern stack I’m eager to work in and contribute to from day one.

During my studies, I focused on systems-level programming, data structures, and software architecture, with projects in C/C++, Python, and JavaScript. I’ve built and tested backend systems in GoLang and Java, collaborated with peers using Git, and practiced clean, maintainable code through object-oriented design. I’m also comfortable learning in fast-paced environments and iterating based on feedback, a skill I developed while working on team projects and open-ended coursework.

What excites me most about Sentry is your open-source philosophy and developer-first mindset. The idea of actively using the tools I help build and making them better for millions of developers is exactly the kind of work I want to be doing. I’d love the chance to learn from your team and contribute meaningfully to your platform.

Thank you for considering my application. I’d be thrilled to grow alongside your engineers and contribute to building tools that make software development better for everyone.

\vspace{0.5cm}

\makeletterclosing

\end{document}
