%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

%\usepackage{ebgaramond} % Use the EB Garamond font

%------------------------------------------------

\name{Marcelo Ponce} % Your name

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.
\address{Toronto, ON} % Your address
\address{(587)~$\cdot$~718~$\cdot$~6272 \\ marcelo.ponce.ardon@gmail.com} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% PROFILE SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{University of Toronto} \hfill \textit{2019 - Present} \\
	Honours Bachelor of Science (HBSc)\\
	Computer Science Specialist, Minor in Mathematics \\
%	\begin{rSubsection}{\textbf{Relevant Coursework}}{}{}{}
%		\item CSC207: Software Design
%		\item CSC209: Software Tools and Systems Programming
%		\item MAT102: Introduction to Mathematical Proofs
%		\item MAT223: Linear Algebra I
%	\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Certifications \& Technical Skills}

	\textbf{Certifications:} Smart Serve Certified \hfill \textit{January 2021} \\
	\textbf{Espresso Equipment Operation:} Nuova Simonelli Aurelia Wave II, Nuova Simonelli Mythos One \\
	%\textbf{Programming Languages:} Python, Java, C++ \\
	%\textbf{Tools:} Git, Linux, LaTeX

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Barista}{March 2023 - Present}{Claudia's Coffee}{Toronto, ON}
		\item Prepared custom espresso drinks and specialty seasonal beverages in a fast paced environment, making up to 45 drinks per hour.
		\item Maintained and cleaned equipment daily, ensuring machine longevity and beverage quality.
		\item Adjusted espresso grind at various times throughout the day to maintain consistent shot quality.
		\item Opening and closing independently of supervision, cash handling, ordering inventory, arming alarms.
		\item Developed relationships with customers, connecting management with local businesses.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Barista}{January 2022 - March 2023}{Touti Gelati}{Toronto, ON}
		\item Prepared over 30 beverages and desserts daily, maintaining high quality and presentation standards.
		\item Enhanced customer experience by providing tailored recommendations for gelato and specialty drinks.
		\item Managed inventory for daily operations, ensuring availability of ingredients during peak hours.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Cashier}{April 2020 - January 2022}{Burrito Boyz}{Toronto, ON}
		\item Streamlined order preparation for a 5-person team.
		\item Coordinated team efforts to ensure accurate and timely order fulfillment, resolving any workflow bottlenecks.
		\item Monitored order progress, addressed customer complaints, and ensured a seamless customer experience.
		\item Supported food preparation and assembly during high-demand periods.
        %add a comment about opening and closing alone, indpendent of supervision, keyholder, cash handling, ordering inventory, liasing with poential vendors, arming alarms, dealing in
        %developing relationships with clients, fostering with local community and connecting with neighbouring businesses
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Server \& Host}{June 2018 - April 2020}{The Manor Village}{Calgary, AB}
		\item Managed simultaneous table service for 20+ residents, ensuring dietary needs and preferences were met.
		\item Assisted kitchen staff with food preparation, dishwashing, and overall cleanliness.
		\item Processed cash payments and served alcoholic beverages in compliance with regulations.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}

	\begin{tabular}{@{} >{\bfseries}l @{} l @{}}
		English &| Advanced\\
		Spanish &| Native\\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
