%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape MARCELO PONCE} \\ \vspace{1pt}
    \small Toronto, ON \\
    \small (587)~$\cdot$~718~$\cdot$~6272 $\Diamond$ \href{mailto:marcelo.ponce.ardon@gmail.com}{\underline{marcelo.ponce.ardon@gmail.com}} $\Diamond$
    \href{https://github.com/marceloponceardon}{\underline{github.com/marceloponceardon}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{Mississauga, ON}
      {Honours Bachelor of Science (HBSc) in Computer Science, Minor in Mathematics}{June 2025} \\
      \vspace{8pt}
      \textbf{Relevant Coursework:} \\
      {\it
	      Computer Security,
	      Neural Networks \& Deep Learning,
	      Scalable Computing,
	      Algorithm Design, Analysis \& Complexity,
	      Parallel Programming,
	      Introduction to Information Security,
	      Introduction to Databases,
	      Programming on the Web,
	      Introduction to Software Engineering,
	      Introduction to Algebraic Cryptography

%	      CSC427: Computer Security,
%	      CSC413: Neural Networks \& Deep Learning,
%	      CSC409: Scalable Computing,
%	      CSC373: Algorithm Design, Analysis \& Complexity,
%	      CSC367: Parallel Programming,
%	      CSC347: Introduction to Information Security,
%	      CSC343: Introduction to Databases,
%	      CSC309: Programming on the Web,
%	      CSC301: Introduction to Software Engineering,
%	      MAT302: Introduction to Algebraic Cryptography
      }
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{CTF427} $\Diamond$ \textit{\href{https://github.com/marceloponceardon/CTF427}{github.com/marceloponceardon/CTF427}} $\Diamond$ {\footnotesize VirtualBox, Docker, CTFd, Kali Linux}}{\emph{Jan. 2025 -- March 2025}}
          \resumeItemListStart
	  \resumeItem{Ran a competitive Capture the Flag (CTF) event designed to teach students about common security vulnerabilities, exploit techniques and challenges (SQLi, Cryptography, Vulnerable Executables, Forensics).}
	  \resumeItem{Built a vulnerable site which contained the 4 main challenges, used the CTFd platform to host the event with scoreboard, hints and solution walkthroughs.}
	  \resumeItem{Taught students how to use Kali Linux tools (sqlmap, steghide, gdb, ghidra), alonside Linux tools for challenges.}
	  \resumeItem{Hosted the two web applications via Docker containers on a VirtualBox VM.}
          \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{jiu-jitsu-autoscoring} $\Diamond$ \textit{\href{https://github.com/jiu-jitsu-autoscoring}{github.com/jiu-jitsu-autoscoring}} $\Diamond$ {\footnotesize Jupyter, PyTorch, Transformers}}{\emph{Jan. 2025 -- Present}}
          \resumeItemListStart
	  \resumeItem{Developing a 5-step pipeline of machine learning models to automatically score Brazilian Jiu-Jitsu match videos.}
	  \resumeItem{Utilizing PyTorch and HuggingFace Transformers to fine-tune pre-trained models for person detection, pose estimation and classification on a dataset of annotated BJJ matches.}
          \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{jules-ferguson.com} $\Diamond$ \textit{\href{https://github.com/marceloponceardon/jules-ferguson.com}{github.com/marceloponceardon/jules-ferguson.com}} $\Diamond$ {\footnotesize React, Express} }{\emph{June 2024 -- Present}}
	  \resumeItemListStart
	  \resumeItem{Built a personal website for Jules Ferguson, a Toronto-based photographer and sexual health educator.}
	  \resumeItem{Coordinated with client to design and implement a custom React-based website, integrating downloadable CV, portfolio, and contact form.}
	  \resumeItem{Hosted on Vercel and Render.}
	  \resumeItemListEnd
      \resumeProjectHeading
      {\textbf{Opalescence} $\Diamond$ \textit{\href{https://github.com/opalescencelabs}{github.com/opalescencelabs}} $\Diamond$ {\footnotesize GoLang, PostgresSQL, Redis, Google OAuth2.0.}}{\emph{Jan. 2024 -- April 2024}}
          \resumeItemListStart
	  \resumeItem{Co--led a team of 7 to design and build a web-based sharable note-taking application, overseeing backend development.}
	  \resumeItem{Implemented a RESTful API using GoLang (GinGonic) and PostgreSQL (GORM), with hosted Redis for caching.}
	  \resumeItem{Integrated GitHub Actions for CI/CD, Google OAuth2.0 for user authentication.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
	\textbf{Programming Languages:} C/C++, Bash/Shell, Python, JavaScript, Java, GoLang, C\#, SQL, HTML/CSS\\
	\textbf{Tools \& Technologies:} Wireshark, sqlmap, Ghidra, john the ripper, gdb, scikit-learn, Pandas, NumPy, Docker, LaTeX, React, Node.js, Redis \\
	\textbf{IDEs \& Editors:} Vim, Visual Studio Code, Eclipse \\
	\textbf{Version Control:} Git, GitHub \\
	\textbf{Databases:} PostgreSQL, MySQL, SQLite, Cassandra, Redis\\
	\textbf{CI/CD:} Github Actions \\
	\textbf{Other Skills \& Tools:} Linux, Data Modeling, Automated Testing, Amazon Web Services (AWS) Agile Development, Scrum
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Barista}{\emph{March 2023 -- Present}}
      {Claudia's Coffee}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Prepared custom espresso drinks and specialty seasonal beverages in a fast paced environment, making up to 45 drinks per hour.}
%	\resumeItem{Maintained and cleaned equipment daily, ensuring machine longevity and beverage quality.}
%	\resumeItem{Adjusted espresso grind at various times throughout the day to maintain consistent shot quality.}
	\resumeItem{Opening and closing independently of supervision, cash handling, ordering inventory, arming alarms.}
	\resumeItem{Developed relationships with customers, connecting management with local businesses.}
      \resumeItemListEnd

%    \resumeSubheading
%    {Barista}{\emph{Jan. 2022 -- March 2023}}
%      {Touti Gelati}{Toronto, ON}
%      \resumeItemListStart
%      \resumeItem{Prepared over 30 beverages and desserts daily, maintaining high quality and presentation standards.}
%      \resumeItem{Enhanced customer experience by providing tailored recommendations for gelato and specialty drinks.}
%      \resumeItem{Managed inventory for daily operations, ensuring availability of ingredients during peak hours.}
%      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
