%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - TIGHTER for 1 page
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
	\textbf{\Huge \scshape MARCELO PONCE ARDON} {\footnotesize (they/them)} \\ \vspace{1pt}
	\small \textsc{Toronto, ON} $\Diamond$
    \small \href{mailto:marcelo.ponce@alumni.utoronto.ca}{\underline{marcelo.ponce@alumni.utoronto.ca}} $\Diamond$
    \href{https://github.com/marceloponceardon}{\underline{github.com}} $\Diamond$ (587)~$\cdot$~718~$\cdot$~6272
\end{center}

%-----------HIGHLIGHTS OF QUALIFICATIONS-----------
\section{\textbf{HIGHLIGHT OF QUALIFICATIONS}}
{\small
	\resumeItemListStart
	  \resumeItem{\textbf{Full-stack developer} specializing in TypeScript/Next.js and Python, demonstrated by building Wikigraph3D—an interactive 3D Wikipedia visualization serving 500+ nodes with optimized rendering performance.}
	  \resumeItem{\textbf{Experienced in machine learning pipelines}, shown by developing a 5-step PyTorch model using HuggingFace Transformers for automated Brazilian Jiu-Jitsu match scoring.}
	  \resumeItem{\textbf{Proficient in scalable backend architecture}, evidenced by co-leading a team of 7 to build a RESTful API with GoLang, PostgreSQL, Redis caching, and CI/CD automation.}
	  \resumeItem{\textbf{Passionate about knowledge transfer and security}, as shown by running a competitive CTF event teaching 20+ students about vulnerabilities, exploitation techniques, and Kali Linux tools.}
	  \resumeItem{\textbf{Practical IT experience} implementing security solutions including organization-wide Bitwarden 2FA deployment and anti-virus rollout across 14+ devices.}
	\resumeItemListEnd
}

%-----------EDUCATION-----------
\section{\textbf{EDUCATION}}
\resumeSubHeadingListStart
  \resumeProjectHeading
  {\textbf{Honours Bachelor of Science (HBSc) in Computer Science} $\Diamond$ University of Toronto}{\emph{June 2025}} \\
  \vspace{4pt}
  \emph{Relevant Coursework}: {\small Software Engineering, Web Programming, Scalable Computing, Parallel Programming, Computer Security, Neural Networks \& Deep Learning, Algorithm Design \& Complexity}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\textbf{PROJECTS}}
  \resumeSubHeadingListStart
	\resumeProjectHeading{\textbf{\href{https://github.com/marceloponceardon/wikigraph3d}{Wikigraph3D}} $\Diamond$ {\footnotesize Next.js, TypeScript, Tailwind CSS, react-force-graph-3d}}{\emph{Aug. 2025 -- Present}}
	\resumeItemListStart
	    \resumeItem{Built interactive 3D Wikipedia graph visualization enabling spatial exploration of 500+ interconnected article-nodes.}
	    \resumeItem{Configured automated code quality tooling (TypeScript strict mode, ESLint, Prettier, Husky pre-commit hooks).}
	    \resumeItem{Optimized rendering performance by caching sprites, preventing unnecessary re-renders during node interactions.}
	\resumeItemListEnd

	\resumeProjectHeading{\textbf{\href{https://github.com/jiu-jitsu-autoscoring}{jiu-jitsu-autoscoring}} $\Diamond$ {\footnotesize Python, Jupyter, PyTorch, Transformers}}{\emph{Jan. 2025 -- Present}}
        \resumeItemListStart
	  \resumeItem{Developing 5-step ML pipeline to automatically score Brazilian Jiu-Jitsu match videos using computer vision.}
	  \resumeItem{Fine-tuning pre-trained PyTorch models via HuggingFace Transformers for person detection, pose estimation, and classification on annotated BJJ dataset.}
        \resumeItemListEnd

	\resumeProjectHeading{\textbf{\href{https://github.com/marceloponceardon/CTF427}{CTF427}} $\Diamond$ {\footnotesize VirtualBox, Docker, CTFd, Kali Linux}}{\emph{Jan. 2025 -- March 2025}}
        \resumeItemListStart
	  \resumeItem{Ran competitive CTF event teaching 20+ students about security vulnerabilities (SQLi, cryptography, binary exploitation, forensics).}
	  \resumeItem{Built vulnerable web applications and hosted via Docker containers on VirtualBox VM with CTFd scoreboard platform.}
        \resumeItemListEnd

	\resumeProjectHeading{\textbf{\href{https://github.com/opalescencelabs}{Opalescence}} $\Diamond$ {\footnotesize GoLang, PostgreSQL, Redis, OAuth2.0}}{\emph{Jan. 2024 -- April 2024}}
        \resumeItemListStart
	  \resumeItem{Co-led team of 7 building web-based note-taking application, overseeing backend architecture and development.}
	  \resumeItem{Implemented RESTful API with GoLang (GinGonic), PostgreSQL (GORM), Redis caching, GitHub Actions CI/CD, and Google OAuth2.0 authentication.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\textbf{EXPERIENCE}}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{IT Administrative Support} $\Diamond$ CANVAS Programs}{\emph{Sept. 2025 -- Present}}
    \resumeItemListStart
      \resumeItem{Deployed organization-wide security solutions: Bitwarden password manager with 2FA and anti-virus across 14+ devices.}
      \resumeItem{Managed user account lifecycle, access controls, and daily troubleshooting for hardware/software issues.}
    \resumeItemListEnd

  \resumeProjectHeading{\textbf{Barista} $\Diamond$ Claudia's Coffee}{\emph{March 2023 -- Present}}
    \resumeItemListStart
      \resumeItem{Prepared 45+ specialty drinks per hour in fast-paced environment; independently managed opening/closing operations.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{\textbf{SKILLS}}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
	\textbf{Languages:} Python, TypeScript/JavaScript, GoLang, C/C++, Java, C\#, SQL, Bash, HTML/CSS\\
	\textbf{Frameworks \& Libraries:} Next.js, React, Node.js, PyTorch, scikit-learn, Pandas, NumPy\\
	\textbf{Tools \& Technologies:} Docker, Git, GitHub Actions, Jupyter, LaTeX\\
	\textbf{Databases:} PostgreSQL, MySQL, Redis, SQLite, Cassandra\\
	\textbf{Other:} AWS, Linux, Agile/Scrum, Automated Testing\\
	$\Diamond$ \textit{Fluent: English, Spanish}\\
  }}
\end{itemize}

\end{document}
